\TheTitle

### 2017-06-30 paper/results.tex
moving figures
Moving correctness figures to different directory

All questions from the study, with the exception of the questions
regarding which modules are changed in a merge tree, show conclude with
rejecting the null hypothesis that there is no difference in correctness
when using gitk versus \tool. Further explanations of the results are
found in the following subsections.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-3.pdf}
  \caption{Correctness of participants using \tool versus gitk
    when determining the series of merges involved with merging a given
  commit}
  \label{fig:q_3_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-4.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which other commits are merged into the master branch
    with this commit}
  \label{fig:q_4_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-5.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining the number of authors involved in a merge tree}
  \label{fig:q_5_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-6.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining who contributed the most changes to a merge tree}
  \label{fig:q_6_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-7.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining how many files were modified in a merge tree}
  \label{fig:q_7_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-8.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which file(s) had the most changes a merge tree}
  \label{fig:q_8_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correct_question-9.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which modules were involved with a merge tree}
  \label{fig:q_9_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/summarize_tool_outcomes.pdf}
  \caption{Correctness of participants across all summarization
    questions of participants using \tool versus gitk, including the
    number of instances of giving up on a task, making a random guess,
    or replying with infinity.}
  \label{fig:summarization_correctness}
\end{figure}

>>>>

All questions from the study, with the exception of the questions
regarding which modules are changed in a merge tree, show conclude with
rejecting the null hypothesis that there is no difference in correctness
when using gitk versus \tool. We do not see a change in these
conclusions if we include continuity correction. Further explanations of
the results are found in the following subsections.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-3.pdf}
  \caption{Correctness of participants using \tool versus gitk
    when determining the series of merges involved with merging a given
  commit}
  \label{fig:q_3_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-4.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which other commits are merged into the master branch
    with this commit}
  \label{fig:q_4_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-5.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining the number of authors involved in a merge tree}
  \label{fig:q_5_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-6.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining who contributed the most changes to a merge tree}
  \label{fig:q_6_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-7.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining how many files were modified in a merge tree}
  \label{fig:q_7_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-8.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which file(s) had the most changes a merge tree}
  \label{fig:q_8_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/question-9.pdf}
  \caption{Correctness of participants using \tool versus gitk when
    determining which modules were involved with a merge tree}
  \label{fig:q_9_correctness}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/correctness/summarize_tool_outcomes.pdf}
  \caption{Correctness of participants across all summarization
    questions of participants using \tool versus gitk, including the
    number of instances of giving up on a task, making a random guess,
    or replying with infinity.}
  \label{fig:summarization_correctness}
\end{figure}
